% ---------------------------------------------------
% ----- Appendix of the template
% ----- for Bachelor-, Master thesis and class papers
% ---------------------------------------------------
%  Created by C. Müller-Birn on 2012-08-17, CC-BY-SA 3.0.
%  Freie Universität Berlin, Institute of Computer Science, Human Centered Computing. 
%

\chapter{Appendix}
\label{ch:Appendix}

\section{Personas}
\label{app:personas}


% Persona 1
\subsection{John - Purple Experience Product Developer}
\label{subsec:persona:productdev}
\subsubsection{Background and Skills}
John (34) is a senior Angular Web Developer at Sprylab, working there for two years. He was born in Berlin and lives in Lichterfelde with his wife and mostly works from home. He is passionate about Angular, Typescript and Developer Experience in general, studied Computer Science at the Beuth Hochschule and hosts Angular conferences.
\\
\subsubsection{Goals and work with the Editor}
\begin{itemize}
  \item Test newly developed features and the related configurations
  \item Configure test apps for development and QA purposes
  \item Support in case Project Developers like <TODO> encounter problems
  \item John works with the editor multiple times a week
\end{itemize}

\hrule
% Persona 2
\subsection{Steffi - Project Developer}
\label{subsec:persona:projectdev}
\subsubsection{Background and Skills}
Steffi (23) studies media informatics and works as a working student at Sprylab since a year. This is her first job in the industry and she is learning new things every day. Her skills include writing CSS and understanding modern web technologies, but she still struggles using native and custom debugging tools if something goes wrong.  
\\
\subsubsection{Goals and work with the Editor}
\begin{itemize}
  \item Configure new apps based on existing templates and adapt them to customer's requirements
  \item Add new components or change data sources for existing apps
  \item Add custom HTML pages or Javascript snippets to intergrate external services
  \item Change styles, color schemas or icons when a customer has a rebranding
  \item Steffi uses the editor as a primary tool for her work
\end{itemize}

\hrule
% Persona 2
\subsection{Karsten - IT department at a publishing house}
\label{subsec:persona:itpublishing}
\subsubsection{Background and Skills}
Karsten (46) worked in the publishing industry for 20 years, but only during the last years his company, aga magazine publisher, tries to catch up with the digital development and trends. He is still struggling with his role and is thankful for every trick or tool that makes his life managing the digital products easier.
\\
\subsubsection{Goals and work with the Editor}
\begin{itemize}
  \item Exchange logos and colors when the magazines he supervies get a redesign
  \item Add new ads to different views when a new campaign starts
  \item Manage URLs to external sites when they change
  \item Karsten uses the Editor once a month on average
\end{itemize}


\section{Zweiter Teil Appendix}
\label{app:second_appendix}  

