% ---------------------------------------------------
% ----- Conclusion of the template
% ----- for Bachelor-, Master thesis and class papers
% ---------------------------------------------------
%  Created by C. Müller-Birn on 2012-08-17, CC-BY-SA 3.0.
%  Freie Universität Berlin, Institute of Computer Science, Human Centered Computing. 
%
\chapter{Conclusion and outlook}
\label{chap:conclusion}      
This thesis demonstrates the challenges and opportunities of applying HCI principles and methods in a brownfield software development project through the full-scale edevelopment of a UI Editor for a digital publishing company, Sprylab.
During the process, it was shown how common user research methods can be adapted to this specific case study and how technical limits and needs of users can be combined in this context.

The challenge was not to just focus on the understanding of technical processes that is a matter of course for a computer scientist, but to research the individual needs of the differently trained and socialized users without prejudice. In addition, technical and commercial constraints of Sprylab had to be taken into account, as well as legal requirements, e.g. when collecting personal data.
\\\\
Various responses expressed that the interviews in particular prompted the participants to consciously reflect on disruptive but also helpful features of the UI Editor. This also ensured build on existing mental models the users have of editors of various kinds. 
The consistently positive feedback shows that the chosen methods and features derived from their outcome were the right approach to enhance the user experience.
Also, the way users were involved during the whole process led to a high level of acceptance and interest in supporting the project.
Additionally, this thesis can help to argue for the use of HCI methods in future projects started at Sprylab as well.
I'm confident that this new software is a stable and extensible tool, especially regarding the two factors Usability and Time-on-Task.
In addition to increasing user satisfaction, it also leads to enhancing productivity and customer satisfaction.
\\\\
However, there is still room for improvements regarding accessibility and usability for users with lower knowledge levels.
The entry hurdle is still high and a lot of background knowledge is assumed, which is partly due to the complexity of other systems in the ecosystem that were set as technical requirements from the beginning on.
Moving forward, replacing the JSON editor with a custom implementation that combines JSON Schemata and generated UI is one of the next steps, which will speed up the user's
workflow even more and allow for further improvements that are impossible with a third-party library.
\\\\
Overall, this thesis has demonstrated the importance of considering HCI principles and methods in brownfield software development projects, and the potential benefits that can be achieved when these approaches are applied in a real-world context.